Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-06 paper.tex
recompiled document
added a caption
writing for string editing section

\begin{figure}\centering
  \includegraphics[width = 7cm]{figures/symbolicRegression.png}
  \caption{DSL learning curve for symbolic regression.}\label{regressionLearningCurve}
\end{figure}
\subsection{String editing}\label{textSection}
\begin{table}

  \centering
  \begin{tabular}{l}
  \toprule
    \texttt{0}, \texttt{+1},\texttt{-1}\\
    \texttt{split}, \texttt{join}, \texttt{map}, \texttt{length}, \texttt{slice}\\
    \texttt{append}, \texttt{chr->str}, \texttt{trim}\\
    \texttt{lowercase}, \texttt{uppercase}, \texttt{capitalize}\\
    \texttt{""},    \texttt{","},     \texttt{" "},    \texttt{"<"}, \texttt{">"}  
  \\\bottomrule
  \end{tabular}
  \caption{Initial set of primitives provided to the system for learning string editing programs}
  \end{table}
\begin{figure}

  \includegraphics[width = 9cm]{figures/text.png}

@@

>>>>

\begin{figure}\centering
  \includegraphics[width = 7cm]{figures/symbolicRegression.png}
  \caption{DSL learning curve for symbolic regression.}\label{regressionLearningCurve}
\end{figure}

\subsection{String editing}\label{textSection}
Synthesizing programs that manipulate strings is a classic problem in the
programming languages and AI literatures~\cite{menon2013machine,lau2001programming},
and algorithms that learn string editing programs ship in Microsoft Excel~\cite{gulwani2011automating}.
However, this prior work presumes a ready-made DSL,
expertly crafted to suit string editing.
We show in this experiment that we can instead start out with a
more restricted set of primitives -- close to the string routines provided by Python --
and automatically recover many of the higher-level building blocks that have made these
other system successful.
Table~\ref{textPrimitives} lists the primitive functions provided to \system.
Absent are any routines for searching for characters, extracting substrings,
or replacing one character with another.
Instead, we provide array/string indexing primitives (\texttt{slice}, \texttt{index}),
basic arithmetic, and functions for splitting a string into a list (\texttt{split})
or turning a list into a string (\texttt{join}).

We automatically generated 600 string editing problems,
along with input/output examples (Figure~\ref{exampleTextProblem}).

\begin{table}

  \centering
  \begin{tabular}{l}
  \toprule
    \texttt{0}, \texttt{+1},\texttt{-1}\\
    \texttt{split}, \texttt{join}, \texttt{map}, \texttt{length}, \texttt{slice}\\
    \texttt{append}, \texttt{chr->str}, \texttt{trim}, \texttt{index}\\
    \texttt{lowercase}, \texttt{uppercase}, \texttt{capitalize}\\
    \texttt{""},    \texttt{","},     \texttt{" "},    \texttt{"<"}, \texttt{">"}  
  \\\bottomrule
  \end{tabular}
  \caption{Initial set of primitives provided to the system for learning string editing programs}\label{textPrimitives}
  \end{table}
\begin{figure}

  \includegraphics[width = 7cm]{figures/text.png}
  \caption{Learning curves for string editing programs}\label{textLearningCurve}

@@

\begin{figure}
  \begin{tabular}{ll}\toprule
    Input&Output\\\midrule
    kIDY eMSz,zON& 	eM\\
KCQ njp,yzhq 	&nj\\
zeChf zzZ,dtFP 	&zz\\
plbKi fmLcO,ykkOR 	&fm    \\\bottomrule
  \end{tabular}
  \caption{Example string edit problem (left) and the program that our system recovers (right)}\label{exampleTextProblem}
  \end{figure}
